Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-18 Article.tex
update notation array (pas beau)

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french, english]{babel}
\usepackage{cite}
\usepackage{caption}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{subcaption}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french, english]{babel}
\usepackage{cite}
\usepackage{caption}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{subcaption}
\usepackage{array}

@@

\newcolumntype{h}{>{\centering}p{40mm}<{}}

\begin{center}
\begin{figure}
\scriptsize
\begin{tabular}{|h|h|}
  \hline
  \textbf{Notations} & \textbf{Meaning} \tabularnewline
  \hline 
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \tabularnewline
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{S}(t)) $ & Instantaneous available production of agent i (coalition S) at time t \tabularnewline
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time serie of agent i available production values \tabularnewline
  $ \mathcal{P}_{i}\ \ (\mathcal{P}_{S}) $ & Probability distribution of agent i (coalition S) available production values \tabularnewline
  $ \phi \in [0,1] $ & Reliability threshold (fixed by the grid operator) \tabularnewline
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold (fixed by the grid operator) \tabularnewline
  $ P_{S}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition S \tabularnewline
  $ P_{\phi}(S) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \tabularnewline
  $ \mathcal{U}_{\phi,\ P^{MIN}}(S) $ & Utility function \tabularnewline
  $ \tau_{i}(S) \in \mathbb{R}$ & Descision rule for mapping overlaping into disjoint coalitions \tabularnewline
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \tabularnewline
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition (entry of the algorithms) \tabularnewline
  $ CS = \{S_{1},...,S_{N_{COAL}}\} $ & Coalition structure \tabularnewline
  \hline
\end{tabular}
\caption{Model main notations}
\label{Fig89}
\end{figure}
\end{center}
